Lexicalized Domain Representations for Neural Machine Translation

### 2019-05-21 2019/emnlp/sparse.tex
revise the table, write conclusion

\section{Introduction \label{sec:introduction}}
% The problem
Owing to the development of flexible and powerful architectures based on neural networks \cite{Cho14properties,Bahdanau15learning,Ghering17convolutional,Vaswani17attention}, Machine Translation (MT) has made significant progresses over the past years, and constitute to date the standard for most production engines. One issue which repeatedly pops up with MT, be it neural or statistical, is the need to perform training with large parallel corpora, typically consisting of millions of parallel sentences deemed to be as close as possible to the application domain. A lot of the recent research effort has thus focused on developping MT systems in restricted data conditions, for instance building multilingual MTs which enable zero-shot translation \cite{Firat16multiway,Ha16towards,Johnson17google}; or even building systems without any parallel data \cite{Artetxe18unsupervised,Lample18unsupervised}.
Another important scenario for industrial MT systems is to adapt a neural system trained using parallel data in one domain to the peculiarity of other domains. Domain Adaption (DA) in MT is an old issue \cite{Foster07mixture,Axelrod11domain}, which comes in various guises, and for which a number of solutions have been studied (see the recent survey of \cite{Chu18asurvey} for neural MT). The typical setting is \emph{supervised adaptation}, where a (small) amount of data of the target domain of interest is used to fine-tuned the parameters of a system trained on a large amount of texts in a source domain. We study here a different scenario, \emph{multi-domain adaptation} \cite{Sennrich13multidomain,Farajian17multidomain}, where we would like to use heterogenous data sources to train a unique system that would work well for all domains. This allows us to be both data efficient (all data is used to train all domains) and compuationally efficient (we only need to train one domain). In our setting, we assume that the domain of test documents is known.

Multi-domain adaptation is conceptually close to multilingual MT, or more generally to multi-task learning \cite{Caruana97multitask}, and can be approached in a number of ways. We adapt here theideas of \cite{Daume07frustratingly} to neural MT, in an attempt to confine the differences between domains at the lexical level, while the rest of the parameters is shared between domains. Our main hypothesis is that most of the differences between domains take place at the lexical level, due to cross-domain polysemy. By contrast, the deeper layers, which arguably model more abstract linguistic phenomena, are made shareable across domains.
To this end, we make sure to design word embeddings in such that they will contain a generic as well as a domain-specific region. We perform experiments with three domains, two neural architectures and two language pairs and find that our technique can effectively build multi-domain NMT, outperforming several baselines. Our contribution is thus twofold:
\begin{itemize}
\item methods to adapt the ideas of \cite{Daume07frustratingly} for two NMT architectures;
\item experimental results that demonstrate the effectiveness of this technique;
\item analysis of embeddings
\end{itemize}
\fyTodo{can we train in random order ? can we get away with catastrophic forgetting ?}
\fyTodo{how to analyze the embeddings ? how can we test or claim ?}

@@

We experiment with two language pairs (English-French, English-German) and data originating from three domains, corresponding to texts from three European institutions: from the European Parlement (EPPS) \cite{Koehn05europarl}, the European Medicines Agency (EMEA), and the European Central Bank (ECB) \cite{Tiedemann2009RANLP5}. We randomly split those corpora into training, validation and test sets (see statistics in Table~\ref{tab:Corpora}).\footnote{The EMEA dataset as distributed on the OPUS site contains many duplicates. We therefore report two numbers: the first is comparable to what has been published on earlier studies (eg.\ \cite{Zeng18multidomain}), the second one is obtained by making the test set entirely disjoint from the train.} The validation sets are used to chose the best model according to the average BLEU score \cite{Papineni02bleu}. Using internal test sets corresponds to somewhat ideal conditions; for contrast experiments, we also use supplementary test sets from three other domains: the official Khresmoi testset \cite{Khresmoi17test}, which is close to EMEA, News test 2014 \cite{Bojar14findings}, and IWSLT 2010 (Talk track) \cite{Paul10overview}. This enables us to evaluate the loss in performance when the test set is from a domain not seen in training.
% The model is also required to achieve comparable performance to generic model. To do so, we use newstest 2009 and IWSLT 2010 whose contain does not particularly belong to any domain.
\fyDone{Check which corpus are useful}
\begin{table}
  \centering
  \begin{tabular}{ *{4}{|r|}}
    \hline
    Corpus & Train & Dev & Test \\ \hline
    \multicolumn{4}{|l|}{$En \rightarrow Fr$ }\\
    \multicolumn{4}{|l|}{Vocab\. En: 30,165, Fr: 30,398}\\
    \hline
    EMEA  & 1,09M & 1000 & 1000 [300]\\
    ECB    & 0,19M & 1000 & 1000     \\
    EPPS   & 2,0M  & 1000 & 1000  \\ \hline \hline
    \multicolumn{4}{|l|}{$En \rightarrow Ge$}\\
    \multicolumn{4}{|l|}{ Vocab.\ En:30,159, De: 30,698}\\ \hline
    EMEA  & 1,11M & 1000 & 1000 \\
    ECB     &  0,11M & 1000 & 1000  \\
    EPPS   & 1,92M & 1000 & 1000 \\ \hline
\end{tabular}
\caption{Train and test corpora}
\label{tab:Corpora}
\end{table}
To reduce the number of lexical units and make our systems open-vocabulary, we apply Byte-Pair Encoding \cite{Sennrich16BPE} separately for each language with 30,000 merge operations. \fyDone{I need explanations here}

@@

\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc||c|}
\hline
Model & EMEA & EPPS & ECB & Khresmoi & NewsTest2014 & IWSLT2010 & Avg. \\
\hline
\multicolumn{8}{l}{} \\[-9pt]  
\multicolumn{8}{l}{English$\rightarrow$French} \\
\hline
$Mixed$ & 67.69$_{47.60}$ & 37.50 & 53.49 & 34.86 & 28.56 & 25.70 & avg \\
\hline
$FT_{EMEA}$ & 76.77$_{49.43}$ & 17.16 & 11.99 & 29.58 & 11.64 & 11.10 & avg \\
$FT_{EPPS}$ & 20.86 & 37.04 & 24.53 & 31.86 & 28.33 & 11.10 & avg \\
$FT_{ECB}$   & 26.93 & 27.09 & 56.52 & 22.04 & 17.51 & 13.99 & avg \\
\hline
$DC$ & 67.87$_{45.42}$ & 37.31 & 54.14 & 33.63 & 26.52 & 24.81 & avg\\
\hline
$LDR_{oracle}$   & 74.26$_{49.90}$ & 37.67 & 54.07 & 33.85 & 28.11 & 25.70 & avg \\
$LDR^{v2}_{oracle}$   & 74.95$_{49.38}$ & 37.35 & 55.91 & 33.57 & 27.59 & 25.27 & avg \\
$LDR_{generic}$ & 73.97$_{49.54}$ & 37.81 & 53.67 & 34.17 & 28.11 & 25.70 & avg \\
$LDR_{pred}$ & 74.29 $_{49.84}$ & 37.73 & 54.01 & 33.34 & 28.32 & 26 & avg \\
$LDR_{wrong}$ & 72.95$_{49.78}$ & 37.62 & 53.35 & - & - & - & avg\\
  \hline
\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{8}{l}{English $\rightarrow$German} \\
\hline
$Mixed$ & 64.57$_{42.99}$ & 26.47 & 68.67 & 21.77 & 17.04 & 18.85 & avg \\
\hline
$FT_{EMEA}$ & 68.35 & 17.02 & 32.87 & 21.15 & 11.21 & 13.49 & avg\\
$FT_{EPPS}$ & 36.19 & 26.29 & 40.71 & 19.67 & 16.47 & 19.24 & avg \\
$FT_{ECB}$   & 24.72 & 18.36 & 74.05 & 11.31  & 10.8 & 11.00 & avg \\
\hline
$DC$ & 63.48$_{42.98}$ & 26.27 & 66.95 & 21.45 & 16.45 & 18.78 & avg \\
\hline
$LDR_{oracle}$ & 70.9$_{46.12}$ & 26.30 & 68.9 & 21.42 & 16.57 & 18.82 & avg \\
$LDR^{v2}_{oracle}$ & 71.31$_{45.23}$ & 25.98 & 73.74 & 21.6 & 16.37 & 19.2 & avg \\
$LDR_{generic}$ & 70.86$_{45.60}$ & 26.14 & 68.59 & 21.95 & 16.57 & 18.82 & avg\\
$LDR_{pred}$ & 70.89$_{46.12}$ & 26.53 & 68.63 & 21.45 & 16.61 & 19.07 & avg \\
$LDR_{wrong}$ & 69.51$_{43.50}$ & 26.31 & 66.86 & - & - & - & avg \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the Transformer architecture \label{tab:results-trsf}}
\end{table*}

\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc||c|}
\hline
Model & EMEA & EPPS & ECB & Khresmoi & NewsTest2014 & IWSLT2010 & Avg. \\
\hline
\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{8}{l}{English$\rightarrow$French} \\
\hline
$Mixed$               & 65.42$_{45.11}$ & 34.7 & 51.38 & 29.27 & 22.21 & 21.63 & avg \\
\hline
$FT_{EMEA}$     & 72.06 $ $ & 18.62 & 16.78 & 25.88 & 10.94 & 5.73 & avg \\
$FT_{EPPS}$      & 35.47 $ $ & 34.61 & 39.56 & 27.11 & 21.85 & 20.61 & avg \\
$FT_{ECB}$        & 21.93 $ $ & 22.6 & 51.53 & 14.74 & 12.10 & 10.47 & avg \\
\hline
$DC$                   & 68.26 $_{43.76}$ & 35.13 & 50.09 & 27.86 & 20.95 & 21.16 & avg \\
 \hline
$WDCMT$           & 68.76 $_{45.29}$ & 35.71 & 52.75 & 32.03 & 24.63 & 23.28 & avg \\
\hline
$LDR_{oracle}$   & 71.73 $_{46.30}$ & 35.21 & 50.91 & 29.62 & 23.00 & 20.96 & avg\\
$LDR_{generic}$ & 70.59 $_{46.37}$ & 35.22 & 49.68 & 29.51 & 23.00 & 20.96 & avg\\
$LDR_{pred}$        & 72.76 $_{46.35}$ & 35.1 & 50.38 & 30.02 & 23.28 & 21.32 & avg\\
$LDR_{wrong}$   & 62.1 $_{43.29}$ & 34.17 & 48.79 &  - & - & - & avg \\
\hline
\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{8}{l}{English$\rightarrow$German} \\
\hline
$Mixed$               & 57.37 $_{37.94}$ & 23.1 & 63.54 & 17.39 & 11.51 & 14.29 & avg\\
\hline
$FT_{EMEA}$      & 65.64 $ $ & 12.36 & 15.93 & 15.38 & 6.22 & 7.6  & avg\\
$FT_{EPPS}$       & 24.90 $ $ & 22.98 & 26.26 & 13.55 & 11.33 & 14.32 & avg \\
$FT_{ECB}$         & 41.8 $ $ & 15.97 & 71.07 & 10.77 & 7.66 & 8.07 & avg\\
\hline
$DC$                    & 62.53 $_{39.25}$ & 23.74 & 65.71 & 16.88 & 11.15 & 14.97 & avg\\
\hline
WDCMT               & 64.05 $_{38.54}$ & 22.82 & 67.00 & 15.94 & 11.45 & 13.66 & avg\\
\hline
$LDR_{oracle}$   & 63.43 $_{40.04}$ & 22.66 & 64.40 & 16.99 & 11.45 & 14.26 & avg\\
$LDR^{v2}_{oracle}$   & 63.27 $_{38.16}$ & 21.83 & 69.55 & 15.7 & 11.32 & 13.98 & avg\\
$LDR_{generic}$ & 63.27 $_{39.75}$ & 22.62 & 63.70 & 17.26 & 11.45 & 14.26 & avg\\
$LDR_{pred}$        & 63.17 $_{39.92}$ & 22.51 & 64 & 15.94 & 11.32 & 14.27 & avg\\
$LDR_{wrong}$   & 56.84 $_{37.05}$ & 22.06 & 61.66 & - & - & - & avg \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the RNN architecture \label{tab:results-rnn}}
\end{table*}
% \clearfloat

>>>>

\section{Introduction \label{sec:introduction}}
% The problem
Owing to the development of flexible and powerful architectures based on neural networks \cite{Cho14properties,Bahdanau15learning,Ghering17convolutional,Vaswani17attention}, Machine Translation (MT) has made significant progresses over the past years, and constitute to date the standard for most production engines. One issue which repeatedly pops up with MT, be it neural or statistical, is the need to perform training with large parallel corpora, typically consisting of millions of parallel sentences deemed to be as close as possible to the application domain. A lot of the recent research effort has thus focused on developping MT systems in restricted data conditions, for instance building multilingual MTs which enable zero-shot translation \cite{Firat16multiway,Ha16towards,Johnson17google}; or even building systems without any parallel data \cite{Artetxe18unsupervised,Lample18unsupervised}.
Another important scenario for industrial MT systems is to adapt a neural system trained using parallel data in one domain to the peculiarity of other domains. Domain Adaption (DA) in MT is an old issue \cite{Foster07mixture,Axelrod11domain}, which comes in various guises, and for which a number of solutions have been studied (see the recent survey of \cite{Chu18asurvey} for neural MT). The typical setting is \emph{supervised adaptation}, where a (small) amount of data of the target domain of interest is used to fine-tuned the parameters of a system trained on a large amount of texts in a source domain. We study here a different scenario, \emph{multi-domain adaptation} \cite{Sennrich13multidomain,Farajian17multidomain}, where we would like to use heterogenous data sources to train a unique system that would work well for all domains. This allows us to be both data efficient (all data is used to train all domains) and computationally efficient (we only train one system). In our setting, we assume that the domain of test documents is known.

Multi-domain adaptation is conceptually close to multilingual MT, or more generally to multi-task learning \cite{Caruana97multitask}, and can be approached in a number of ways. We adapt here theideas of \cite{Daume07frustratingly} to neural MT, in an attempt to confine the differences between domains at the lexical level, while the rest of the parameters is shared between domains. Our main hypothesis is that most of the differences between domains take place at the lexical level, due to cross-domain polysemy. By contrast, the deeper layers, which arguably model more abstract linguistic phenomena, are made shareable across domains.
To this end, we make sure to design word embeddings in such that they will contain a generic as well as a domain-specific region. We perform experiments with three domains, two neural architectures and two language pairs and find that our technique can effectively build multi-domain NMT, outperforming several baselines. Our contribution is thus as follows
\begin{itemize}
\item we develop methods to adapt the ideas of \cite{Daume07frustratingly} for two NMT architectures;
\item we provide experimental evidence that suggest the effectiveness of this technique;
\item our analysis of embeddings seems to confort our assumption that their variation across domain actually reflects a variation of senses.
\end{itemize}
\fyDone{can we train in random order ? can we get away with catastrophic forgetting ?}
\fyDone{how to analyze the embeddings ? how can we test or claim ?}

@@

We experiment with two language pairs (English-French, English-German) and data originating from three domains, corresponding to texts from three European institutions: from the European Parlement (EPPS) \cite{Koehn05europarl}, the European Medicines Agency (EMEA), and the European Central Bank (ECB) \cite{Tiedemann2009RANLP5}. We randomly split those corpora into training, validation and test sets (see statistics in Table~\ref{tab:Corpora}).\footnote{The EMEA dataset as distributed on the OPUS site contains many duplicates. We therefore report two numbers: the first is comparable to what has been published on earlier studies (eg.\ \cite{Zeng18multidomain}), the second one is obtained by making the test set entirely disjoint from the train.} The validation sets are used to chose the best model according to the average BLEU score \cite{Papineni02bleu}. Using internal test sets corresponds to somewhat ideal conditions; for contrast experiments, we also use supplementary test sets from three other domains: the official Khresmoi testset \cite{Khresmoi17test}, which is close to EMEA, News test 2014 \cite{Bojar14findings}, and IWSLT 2010 (Talk track) \cite{Paul10overview}. This enables us to evaluate the loss in performance when the test set is from a domain not seen in training.
% The model is also required to achieve comparable performance to generic model. To do so, we use newstest 2009 and IWSLT 2010 whose contain does not particularly belong to any domain.
\fyDone{Check which corpus are useful}
\begin{table}
  \centering
  \begin{tabular}{ *{4}{|r|}}
    \hline
    Corpus & Train & Dev & Test \\ \hline
    \multicolumn{4}{|l|}{En $\rightarrow$ Fr }\\
    \multicolumn{4}{|l|}{Vocabulary size - En: 30,165, Fr: 30,398}\\
    \hline
    EMEA  & 1,09M & 1000 & 1000$_{300}$\\
    ECB    & 0,19M & 1000 & 1000     \\
    EPPS   & 2,0M  & 1000 & 1000  \\ \hline \hline
    \multicolumn{4}{|l|}{En $\rightarrow$ De}\\
    \multicolumn{4}{|l|}{Vocabulary size -  En:30,159, De: 30,698}\\ \hline
    EMEA  & 1,11M & 1000 & 1000$_{300}$ \\
    ECB     &  0,11M & 1000 & 1000  \\
    EPPS   & 1,92M & 1000 & 1000 \\ \hline
\end{tabular}
\caption{Train and test corpora}
\label{tab:Corpora}
\end{table}
To reduce the number of lexical units and make our systems open-vocabulary, we apply Byte-Pair Encoding \cite{Sennrich16BPE} separately for each language with 30,000 merge operations. \fyDone{I need explanations here}

@@

\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc||c|}
\hline
Model & EMEA & EPPS & ECB & Khresmoi & NewsTest2014 & IWSLT2010 & Avg. \\
\hline
\multicolumn{8}{l}{} \\[-9pt]  
\multicolumn{8}{l}{English$\rightarrow$French} \\
\hline
$Mixed$ & 67.69$_{47.60}$ & 37.50 & 53.49 & 34.86 & 28.56 & 25.70 & avg \\
\hline
$\mathtt{FT} (EMEA)$ & 76.77$_{49.43}$ & 17.16 & 11.99 & 29.58 & 11.64 & 11.10 & avg \\
$\mathtt{FT} (EPPS)$  & 20.86 & 37.04 & 24.53 & 31.86 & 28.33 & 11.10 & avg \\
$\mathtt{FT} (ECB)$   & 26.93 & 27.09 & 56.52 & 22.04 & 17.51 & 13.99 & avg \\
\hline
$DC$ & 67.87$_{45.42}$ & 37.31 & 54.14 & 33.63 & 26.52 & 24.81 & avg\\
\hline
$LDR_{oracle}$   & 74.26$_{49.90}$ & 37.67 & 54.07 & 33.85 & 28.11 & 25.70 & avg \\
$LDR^{v2}_{oracle}$   & 74.95$_{49.38}$ & 37.35 & 55.91 & 33.57 & 27.59 & 25.27 & avg \\
$LDR_{generic}$ & 73.97$_{49.54}$ & 37.81 & 53.67 & 34.17 & 28.11 & 25.70 & avg \\
$LDR_{pred}$ & 74.29 $_{49.84}$ & 37.73 & 54.01 & 33.34 & 28.32 & 26 & avg \\
$LDR_{wrong}$ & 72.95$_{49.78}$ & 37.62 & 53.35 & - & - & - & avg\\
  \hline
\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{8}{l}{English $\rightarrow$German} \\
\hline
$Mixed$ & 64.57$_{42.99}$ & 26.47 & 68.67 & 21.77 & 17.04 & 18.85 & avg \\
\hline
$\mathtt{FT} (EMEA)$ & 68.35$_{42.97}$ & 17.02 & 32.87 & 21.15 & 11.21 & 13.49 & avg\\
$\mathtt{FT} (EPPS)$ & 36.19 & 26.29 & 40.71 & 19.67 & 16.47 & 19.24 & avg \\
$\mathtt{FT} (ECB)$  & 24.72 & 18.36 & 74.05 & 11.31  & 10.8 & 11.00 & avg \\
\hline
$DC$ & 63.48$_{42.98}$ & 26.27 & 66.95 & 21.45 & 16.45 & 18.78 & avg \\
\hline
$LDR_{oracle}$ & 70.9$_{46.12}$ & 26.30 & 68.9 & 21.42 & 16.57 & 18.82 & avg \\
$LDR^{v2}_{oracle}$ & 71.31$_{45.23}$ & 25.98 & 73.74 & 21.6 & 16.37 & 19.2 & avg \\
$LDR_{generic}$ & 70.86$_{45.60}$ & 26.14 & 68.59 & 21.95 & 16.57 & 18.82 & avg\\
$LDR_{pred}$ & 70.89$_{46.12}$ & 26.53 & 68.63 & 21.45 & 16.61 & 19.07 & avg \\
$LDR_{wrong}$ & 69.51$_{43.50}$ & 26.31 & 66.86 & - & - & - & avg \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the Transformer architecture \label{tab:results-trsf}}
\end{table*}

\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc||c|}
\hline
Model & EMEA & EPPS & ECB & Khresmoi & NewsTest2014 & IWSLT2010 & Avg. \\
\hline
\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{8}{l}{English$\rightarrow$French} \\
\hline
$Mixed$               & 65.42$_{45.11}$ & 34.7 & 51.38 & 29.27 & 22.21 & 21.63 & avg \\
\hline
$\mathtt{FT} (EMEA)$  & 72.06 $ $ & 18.62 & 16.78 & 25.88 & 10.94 & 5.73 & avg \\
$\mathtt{FT} (EPPS)$    & 35.47 $ $ & 34.61 & 39.56 & 27.11 & 21.85 & 20.61 & avg \\
$\mathtt{FT} (ECB)$     & 21.93 $ $ & 22.6 & 51.53 & 14.74 & 12.10 & 10.47 & avg \\
\hline
$DC$                   & 68.26 $_{43.76}$ & 35.13 & 50.09 & 27.86 & 20.95 & 21.16 & avg \\
 \hline
$WDCMT$           & 68.76 $_{45.29}$ & 35.71 & 52.75 & 32.03 & 24.63 & 23.28 & avg \\
\hline
$LDR_{oracle}$   & 71.73 $_{46.30}$ & 35.21 & 50.91 & 29.62 & 23.00 & 20.96 & avg\\
$LDR_{generic}$ & 70.59 $_{46.37}$ & 35.22 & 49.68 & 29.51 & 23.00 & 20.96 & avg\\
$LDR_{pred}$        & 72.76 $_{46.35}$ & 35.1 & 50.38 & 30.02 & 23.28 & 21.32 & avg\\
$LDR_{wrong}$   & 62.1 $_{43.29}$ & 34.17 & 48.79 &  - & - & - & avg \\
\hline
\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{8}{l}{English$\rightarrow$German} \\
\hline
$Mixed$               & 57.37 $_{37.94}$ & 23.1 & 63.54 & 17.39 & 11.51 & 14.29 & avg\\
\hline
$\mathtt{FT} (EMEA)$  & 65.64$_{44.71}$ & 12.36 & 15.93 & 15.38 & 6.22 & 7.6  & avg\\
$\mathtt{FT} (EPPS)$   & 24.90 $ $ & 22.98 & 26.26 & 13.55 & 11.33 & 14.32 & avg \\
$\mathtt{FT} (ECB)$    & 41.8 $ $ & 15.97 & 71.07 & 10.77 & 7.66 & 8.07 & avg\\
\hline
$DC$                    & 62.53 $_{39.25}$ & 23.74 & 65.71 & 16.88 & 11.15 & 14.97 & avg\\
\hline
WDCMT               & 64.05 $_{38.54}$ & 22.82 & 67.00 & 15.94 & 11.45 & 13.66 & avg\\
\hline
$LDR_{oracle}$   & 63.43 $_{40.04}$ & 22.66 & 64.40 & 16.99 & 11.45 & 14.26 & avg\\
$LDR^{v2}_{oracle}$   & 63.27 $_{38.16}$ & 21.83 & 69.55 & 15.7 & 11.32 & 13.98 & avg\\
$LDR_{generic}$ & 63.27 $_{39.75}$ & 22.62 & 63.70 & 17.26 & 11.45 & 14.26 & avg\\
$LDR_{pred}$        & 63.17 $_{39.92}$ & 22.51 & 64 & 15.94 & 11.32 & 14.27 & avg\\
$LDR_{wrong}$   & 56.84 $_{37.05}$ & 22.06 & 61.66 & - & - & - & avg \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the RNN architecture \label{tab:results-rnn}}
\end{table*}
% \clearfloat
